Self Regulation Ontology Retest Data Report

### 2017-04-28 SRO_Report.Rmd
changed gitignore to not add bootstrapped results

Bootstrapping everything at once in this way locally would take around four hours.
```{r eval=FALSE}
as.data.frame(numeric_cols) %>%
  mutate(index = 1:n()) %>%
  group_by(index) %>%
  # rowwise()%>% #this works too but the output is nicer the other way
  do(plyr::rdply(2, bootstrap_relialibility(dv_var = as.character(.$numeric_cols), metric = c("icc", "spearman"))))

>>>>

Bootstrapping everything at once in this way locally would take around four hours.
```{r eval=FALSE}
non_hddm_numeric_cols=numeric_cols[-grep("hddm", numeric_cols)]

boot_df = as.data.frame(non_hddm_numeric_cols) %>%
  mutate(index = 1:n()) %>%
  group_by(index) %>%
  do(plyr::rdply(10, bootstrap_relialibility(dv_var = as.character(.$non_hddm_numeric_cols))))

boot_df
```
